Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-13 main.Rmd
include examples of periodic and quasi-periodic

\todo[inline]{Give an example}

@@

\todo[inline]{Give an example}

>>>>

```{r group-periodicial, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$."}
knitr::include_graphics("Figs/groups_periodically.png")
```

@@

```{r quasi-group-periodicial, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$ with $E1$ as the exception."}
knitr::include_graphics("Figs/quasi_groups_periodically.png")
```
